%Everything on these pages needs to be lower Roman numeral

% Front Page
\title{\bf {\LARGE Using Evolutionary Computing to Develop Game Strategy for a Non-Deterministic Game}}
\author{by \\ Kevin Mukhar \\  B.A., University of Washington, 1983 \\ 
M.S., University of Northern Colorado, 1993 
\\
\\
\\ A thesis submitted to the Graduate Faculty of the \\
University of Colorado at Colorado Springs \\
in partial fulfillment of the \\
requirements for the degree of \\
Master of Science \\
Department of Computer Science \\
2013 }
\date{}

\maketitle

\setcounter{page}{2}

%Copyright Page
\newpage

\pagestyle{plain}

\begin{minipage}[t]{5.0in}
	\vspace{7.0in}
	\bf \copyright \ Copyright By Kevin Mukhar 2013 \\[-1.0pc]
	Some Rights Reserved (See Appendix~\ref{appendix:licensesummary}) \rm
\end{minipage}



%Signatures Page
\newpage

\begin{center}
	This thesis for the Master of Science degree by \\
	Kevin Mukhar \\
	has been approved for the \\
 	Department of Computer Science \\
	by \\ 
	\vspace{3.0pc}
	\makebox[3in]{\hrulefill} \\[-1.0pc]
	Jugal Kalita, Chair \\
	\vspace{3.0pc}
	\makebox[3in]{\hrulefill} \\[-1.0pc] 
	Sudhanshu Semwal \\
	\vspace{3.0pc}
	\makebox[3in]{\hrulefill} \\[-1.0pc] 
	Rory Lewis \\
\end{center}


\begin{flushright}
	\vspace{2.0pc}
	\makebox[2in]{\hrulefill} \\[-1.0pc]
	Date
\end{flushright}


%Abstract
\newpage

\setlength{\parindent}{0in}
Mukhar, Kevin (M.S., Computer Science) 

Using Evolutionary Computing to
Develop Game Strategy for a Non-Deterministic Game 

Thesis directed by Professor Jugal Kalita

\vspace{28pt}
\setlength{\parindent}{.4in}

Games and game theory are rich fields of study for artificial intelligence (AI)
and evolutionary computation. It is known that games can be used to teach
knowledge and skills. Games can also be used to model real-world situations. If
humans, or other animals, can learn to play games successfully, it is
reasonable to theorize that a computational based AI can also learn to play
games. A great deal of research has been conducted into using AI to solve
deterministic games with complete information. However, less research has
been conducted into non-deterministic games. This thesis investigates the use of
evolutionary computation techniques to evolve game strategies for the
multi-player non-deterministic game Monopoly.

%Dedication Page
\newpage

\parbox{5.0in}{
	\vspace{2.0in}
	\begin{center}
		{\large{\emph{Dedicated to my wife Anne\\ who has been waiting much
		too long for me to finish this thesis.}}}
	\end{center}
}


%Acknowledgments
\newpage
\begin{center}
	{\large{\bf Acknowledgments}}
\end{center}
\setlength{\parindent}{.4in}

I wish to thank Dr. Jugal Kalita for his guidance and patience throughout the
project. Like my wife, he has been waiting too long for me to finish this
thesis.

I also wish to thank the following individuals who played numerous games
of Monopoly against the AI players to test whether the players had evolved to a
human level of competition: Anne Mukhar, Barbara Maxwell, Kristen Johnson,
Christine Mukhar, Hillary Lauren, Shirley Mukhar, Beth Hinchen, Evan Johnson,
Marin Johnson, Greg Bergquist, Luis Angel-Mex, and Tom Hinchen.