\clearpage
\newpage
\chapter{Introduction}\label{chap:intro}
Games can be used to study many different real world problems. In the
classic monograph by John Von Neumann and Oskar Morgenstern, \emph{Theory of
Games and Economic Behavior}, it was applied to economics and economic behavior
\cite{neumann1944theory}.

Early work by mathematicians studying card and dice games led to the development
of statistics and probability~\cite{hald1990history,rudas2008handbook}. Games
can be studied from a sociological point of view, looking at how social behavior
and human interactions affect and are affected by game
play~\cite{fararo1992meaning}. Artificial intelligence researchers have
experimented with developing AI game players and finding optimum game
strategies~\cite{russell2010artificial}.

\section{Objective}

Early research into AI and games tended to focus on developing algorithms for
searching the space of legal moves. This research led to such techniques as the
Min-Max algorithm~\cite{neumann1944theory} and the A* search
algorithm~\cite{Hart_Nilsson_Raphael_1968,Hart:1972:LFB:1056777.1056779}. The
Min-Max algorithm was originally developed by Von Neumann as a way to develop
the best move in a 2-person zero-sum game with complete information. Although
originally developed for a 2-person game, the min-max theorem has been extended
to cover any number of players. The A* algorithm is a method to find the least
cost path in traversing a search space or graph.

With the development of genetic algorithms and evolutionary computation,
re\-search\-ers in this area have investigated many games in attempts to show
that optimal strategies for games can be evolved. Much of that research has
focused on two player deterministic games like The Prisoner's
Dilemma~\cite{Flood1958} and Tic-Tac-Toe. Evolutionary computation techniques
have been used with good success for these types of
problems~\cite{DBLP:conf/cig/QuekG07,Fogel1993}.

There are other classes of games, however, such as multi-player
non-deterministic games where the search space is potentially quite large and
the cost function could have multiple local and global
optima~\cite{condon1992complexity,condon1993algorithms,Walker:gamebe:2011}. Any
game that relies on some form of non-determinism (i.e., rolling dice, shuffling
cards, etc.) falls into this category. Evolutionary computation could be an
effective approach to these types of problems because it provides the capability
to traverse a large search space and find optimal
strategies~\cite{Quek_GAPoker,Foster1990219,eriksson2001evolution}.

This thesis documents experiments in creating game strategies by evolutionary
computation. In general, the experiments studied whether genetic algorithms can
be used to develop strategies for a non-deterministic game.

\section{Organization of Thesis}

The thesis investigated evolutionary computing as a means to develop game
playing strategies. Since the primary subject matter of this thesis is genetic
algorithms, Chapter~\ref{chap:geneticAlgorithms} starts with a brief overview of
genetic algorithms.

Chapter~\ref{chap:background} provides a survey of some previous research into
evolutionary computation and games that will be applied in this thesis. The chapter
looks at both practical and theoretical research that applied evolutionary
computing to various games.

The game known as Monopoly was chosen as the subject of this research.
Chapter~\ref{chap:monopoly} provides details about Monopoly, focusing on the
rules of the game.

The details of how a genetic algorithm will be used in this research are provided
in Chapter~\ref{chap:algorithm}. In that chapter various formats for the genome,
along with different options for measuring genome fitness, and the process for
propagating a population are presented.

Using the parameters in Chapter~\ref{chap:algorithm}, populations of players are
created and then played in simulated Monopoly tournaments. The populations are
evolved and then they compete again with the goal of generating better players.
The results of the evolutionary process are detailed in
Chapter~\ref{chap:results}.

Chapter~\ref{chap:conclusion} concludes the thesis by summarizing and discussing
the results.
