\clearpage
\chapter{Creative Commons License}
\label{appendix:licensesummary}
% \setlength{\voffset}{0pt} 
% \addtolength{\voffset}{-54pt}
% \setlength{\textheight}{718pt} 
% \setlength{\topmargin}{-12pt}
% \setlength{\headheight}{12pt} 
% \setlength{\headsep}{5pt}
% \setlength{\footskip}{20pt}
%\fontsize{10}{12}\selectfont
This work is licensed under the Creative Commons
Attribution-NonCommercial-NoDerivs 3.0 Unported License. To view a copy of this
license, send a letter to Creative Commons, 444 Castro Street, Suite 900,
Mountain View, California, 94041, USA, or visit
\url{http://creativecommons.org/licenses/by-nc-nd/3.0/}.
\section*{Disclaimer} This is a human-readable summary of the Legal Code (the
full license).
\section*{You are free:}
    \textbf{to Share} - to copy, distribute and transmit the work
\section*{Under the following conditions:}
    \textbf{Attribution} - You must attribute the work in the manner specified
    by the author or licensor (but not in any way that suggests that they
    endorse you or your use of the work).

    \textbf{Noncommercial} - You may not use this work for commercial purposes.

    \textbf{No Derivative Works} - You may not alter, transform, or build upon
    this work.
\section*{With the understanding that:}
    \textbf{Waiver} - Any of the above conditions can be waived if you get
    permission from the copyright holder.

    \textbf{Public Domain} - Where the work or any of its elements is in the
    public domain under applicable law, that status is in no way affected by the
    license.

    \textbf{Other Rights} - In no way are any of the following rights affected
    by the license:
      \begin{itemize}
        \item {Your fair dealing or fair use rights, or other applicable
      copyright exceptions and limitations;}
        \item {The author's moral rights;}
        \item {Rights other persons may have either in the work itself or in how
      the work is used, such as publicity or privacy rights.}
      \end{itemize}

\nopagebreak

\section*{Notice} For any reuse or distribution, you must make clear to others
the license terms of this work.